### 2021-05-19 README.Rmd
additional files dealing with the paper and the final model, slight updates to the plotting functions (added a num_vars argument for limiting the number of variables to 10 by default)

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?token=zA4xhwrbzL7YLqiktuAB&branch=main)](https://travis-ci.com/srmatth/mshap)
[![Codecov test coverage](https://codecov.io/gh/srmatth/mshap/branch/main/graph/badge.svg)](https://codecov.io/gh/srmatth/mshap?branch=main)
<!-- badges: end -->
